Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-12 paper/letter.tex
new reference

The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
will follow a difussion-like process before escaping the galaxy or
being absorbed by dust. This makes it hard to interpret Lyman-alpha
line observations as the reulting profile is sensitive to the
dynamical, chemical and thermal conditions in the interstellar
medium. State-of-the-art models use mon.

It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity.  
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.

>>>>

The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
will follow a difussion-like process before escaping the galaxy or
being absorbed by dust. This makes it hard to interpret Lyman-alpha
line observations as the reulting profile is sensitive to the
dynamical, chemical and thermal conditions in the interstellar
medium. State-of-the-art models use montecarlo radiative transfer
simulations to interpret lya line profiles. Only in very few symmetric
cases analytical solutions are available.

Recent models computational models \cite{GaravitoCamargo2014} have
shown that rotation also imprints an effect on the Lyman-alpha
morphology.  
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity.  
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.
